---
title: "Code book"
author: "Xavier Magaña Vera"
date: "7/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(kableExtra)
library(reshape2)
###################################TEST######################################
X_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/X_test.txt", quote="\"", comment.char="")
y_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/y_test.txt", quote="\"", comment.char="")
subject_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/subject_test.txt", quote="\"", comment.char="")
###################################TRAIN######################################
X_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/X_train.txt", quote="\"", comment.char="")
y_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/y_train.txt", quote="\"", comment.char="")
subject_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/subject_train.txt", quote="\"", comment.char="")
#################################MAIN LABELS###########################################
features <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/features.txt")
activitylabels <-read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/activity_labels.txt")

## Assign names
colnames(X_test) <- features[,2]
colnames(X_train) <- features[,2]

## Assign labels
colnames(y_test) <- "activity"
colnames(y_train) <- "activity"
colnames(subject_test) <- "subjectnum"
colnames(subject_train) <- "subjectnum"
colnames(activitylabels) <- c("subjectnum", "activity")


### Merge data
TRAIN <- cbind(y_train,subject_train, X_train)
TEST <- cbind(y_test,subject_test, X_test)
BDF <- rbind(TRAIN, TEST)

## Getting mean and SD
cnames <- colnames(BDF)
sb <- grep("subjectnum+", cnames, value = TRUE)
a <- grep("activity+", cnames, value=TRUE)
m <- grep("mean+", cnames, value = TRUE)
sd <- grep("std+", cnames, value = TRUE)
v <- c(sb,a,m,sd)
mean_sd <- select(BDF, v)
BDFm_sd <- merge(mean_sd, activitylabels, by.x = "activity", by.y = "subjectnum")

## Activity names (NAMES ARE IN THE LAST COLUMN)
BDFm_sd$activity <- BDFm_sd$activity.y
BDFm_sd <- BDFm_sd[,1:81]

## Rename
newnames <- names(BDFm_sd)
newnames <- sub("^t", "Time", newnames) 
newnames <- sub("^f", "Frequency", newnames)
newnames <- sub("Acc+", "Acceleration", newnames) 
newnames <- sub("Gyro+", "Gyroscope", newnames) 
newnames <- sub("std+", "StandardDeviation", newnames)
colnames(BDFm_sd) <- newnames

## Reshape
DF <- melt(BDFm_sd, id = c("activity", "subjectnum"))
DFfinal <- dcast(DF, activity + subjectnum ~ variable, mean)
```

### Variables 

The final dataset was created with the following variables, I assigned each and every one of them the activity name and the subject that corresponds each activity and substituted some characters for words as shown below:

- t <- Time
- f <- Frequency
- Acc <- Acceleration
- Gyro <- Gyroscope
- std <- StandardDeviation

 [1] "activity"                                                
 [2] "subjectnum"                                              
 [3] "TimeBodyAcceleration-mean()-X"                           
 [4] "TimeBodyAcceleration-mean()-Y"                           
 [5] "TimeBodyAcceleration-mean()-Z"                           
 [6] "TimeGravityAcceleration-mean()-X"                        
 [7] "TimeGravityAcceleration-mean()-Y"                        
 [8] "TimeGravityAcceleration-mean()-Z"                        
 [9] "TimeBodyAccelerationJerk-mean()-X"                       
[10] "TimeBodyAccelerationJerk-mean()-Y"                       
[11] "TimeBodyAccelerationJerk-mean()-Z"                       
[12] "TimeBodyGyroscope-mean()-X"                              
[13] "TimeBodyGyroscope-mean()-Y"                              
[14] "TimeBodyGyroscope-mean()-Z"                              
[15] "TimeBodyGyroscopeJerk-mean()-X"                          
[16] "TimeBodyGyroscopeJerk-mean()-Y"                          
[17] "TimeBodyGyroscopeJerk-mean()-Z"                          
[18] "TimeBodyAccelerationMag-mean()"                          
[19] "TimeGravityAccelerationMag-mean()"                       
[20] "TimeBodyAccelerationJerkMag-mean()"                      
[21] "TimeBodyGyroscopeMag-mean()"                             
[22] "TimeBodyGyroscopeJerkMag-mean()"                         
[23] "FrequencyBodyAcceleration-mean()-X"                      
[24] "FrequencyBodyAcceleration-mean()-Y"                      
[25] "FrequencyBodyAcceleration-mean()-Z"                      
[26] "FrequencyBodyAcceleration-meanFreq()-X"                  
[27] "FrequencyBodyAcceleration-meanFreq()-Y"                  
[28] "FrequencyBodyAcceleration-meanFreq()-Z"                  
[29] "FrequencyBodyAccelerationJerk-mean()-X"                  
[30] "FrequencyBodyAccelerationJerk-mean()-Y"                  
[31] "FrequencyBodyAccelerationJerk-mean()-Z"                  
[32] "FrequencyBodyAccelerationJerk-meanFreq()-X"              
[33] "FrequencyBodyAccelerationJerk-meanFreq()-Y"              
[34] "FrequencyBodyAccelerationJerk-meanFreq()-Z"              
[35] "FrequencyBodyGyroscope-mean()-X"                         
[36] "FrequencyBodyGyroscope-mean()-Y"                         
[37] "FrequencyBodyGyroscope-mean()-Z"                         
[38] "FrequencyBodyGyroscope-meanFreq()-X"                     
[39] "FrequencyBodyGyroscope-meanFreq()-Y"                     
[40] "FrequencyBodyGyroscope-meanFreq()-Z"                     
[41] "FrequencyBodyAccelerationMag-mean()"                     
[42] "FrequencyBodyAccelerationMag-meanFreq()"                 
[43] "FrequencyBodyBodyAccelerationJerkMag-mean()"             
[44] "FrequencyBodyBodyAccelerationJerkMag-meanFreq()"         
[45] "FrequencyBodyBodyGyroscopeMag-mean()"                    
[46] "FrequencyBodyBodyGyroscopeMag-meanFreq()"                
[47] "FrequencyBodyBodyGyroscopeJerkMag-mean()"                
[48] "FrequencyBodyBodyGyroscopeJerkMag-meanFreq()"            
[49] "TimeBodyAcceleration-StandardDeviation()-X"              
[50] "TimeBodyAcceleration-StandardDeviation()-Y"              
[51] "TimeBodyAcceleration-StandardDeviation()-Z"              
[52] "TimeGravityAcceleration-StandardDeviation()-X"           
[53] "TimeGravityAcceleration-StandardDeviation()-Y"           
[54] "TimeGravityAcceleration-StandardDeviation()-Z"           
[55] "TimeBodyAccelerationJerk-StandardDeviation()-X"          
[56] "TimeBodyAccelerationJerk-StandardDeviation()-Y"          
[57] "TimeBodyAccelerationJerk-StandardDeviation()-Z"          
[58] "TimeBodyGyroscope-StandardDeviation()-X"                 
[59] "TimeBodyGyroscope-StandardDeviation()-Y"                 
[60] "TimeBodyGyroscope-StandardDeviation()-Z"                 
[61] "TimeBodyGyroscopeJerk-StandardDeviation()-X"             
[62] "TimeBodyGyroscopeJerk-StandardDeviation()-Y"             
[63] "TimeBodyGyroscopeJerk-StandardDeviation()-Z"             
[64] "TimeBodyAccelerationMag-StandardDeviation()"             
[65] "TimeGravityAccelerationMag-StandardDeviation()"          
[66] "TimeBodyAccelerationJerkMag-StandardDeviation()"         
[67] "TimeBodyGyroscopeMag-StandardDeviation()"                
[68] "TimeBodyGyroscopeJerkMag-StandardDeviation()"            
[69] "FrequencyBodyAcceleration-StandardDeviation()-X"         
[70] "FrequencyBodyAcceleration-StandardDeviation()-Y"         
[71] "FrequencyBodyAcceleration-StandardDeviation()-Z"         
[72] "FrequencyBodyAccelerationJerk-StandardDeviation()-X"     
[73] "FrequencyBodyAccelerationJerk-StandardDeviation()-Y"     
[74] "FrequencyBodyAccelerationJerk-StandardDeviation()-Z"     
[75] "FrequencyBodyGyroscope-StandardDeviation()-X"            
[76] "FrequencyBodyGyroscope-StandardDeviation()-Y"            
[77] "FrequencyBodyGyroscope-StandardDeviation()-Z"            
[78] "FrequencyBodyAccelerationMag-StandardDeviation()"        
[79] "FrequencyBodyBodyAccelerationJerkMag-StandardDeviation()"
[80] "FrequencyBodyBodyGyroscopeMag-StandardDeviation()"       
[81] "FrequencyBodyBodyGyroscopeJerkMag-StandardDeviation()" 

### Final dataset 

The following dataset already has the changed names and corrections of the whole project, it contains 6 observations and 81 variables.

```{r}
kable(DFfinal) %>%
  kable_styling() %>%
  scroll_box(width = "1000px", height = "300px")
```
