---
title: "Code book"
author: "Xavier Magaña Vera"
date: "7/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(kableExtra)
###################################TEST######################################
X_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/X_test.txt", quote="\"", comment.char="")
y_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/y_test.txt", quote="\"", comment.char="")
subject_test <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/test/subject_test.txt", quote="\"", comment.char="")
###################################TRAIN######################################
X_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/X_train.txt", quote="\"", comment.char="")
y_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/y_train.txt", quote="\"", comment.char="")
subject_train <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/train/subject_train.txt", quote="\"", comment.char="")
#################################MAIN LABELS###########################################
features <- read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/features.txt")
activitylabels <-read.table("C:/Users/xavie/OneDrive/Escritorio/data science coursera/UCI HAR Dataset/activity_labels.txt")

## Assign names
colnames(X_test) <- features[,2]
colnames(X_train) <- features[,2]

## Assign labels
colnames(y_test) <- "activity"
colnames(y_train) <- "activity"
colnames(subject_test) <- "subjectnum"
colnames(subject_train) <- "subjectnum"
colnames(activitylabels) <- c("subjectnum", "activity")


### Merge data
TRAIN <- cbind(y_train,subject_train, X_train)
TEST <- cbind(y_test,subject_test, X_test)
BDF <- rbind(TRAIN, TEST)


## Getting mean and SD
cnames <- colnames(BDF)
mean_sd <- (grepl("subjectnum", cnames) | grepl("activity", cnames) | grepl("mean..", cnames) | grepl("std..", cnames))
BDFm_sd <- BDF[ , mean_sd == TRUE]

## Activity names (NAMES ARE IN THE LAST COLUMN)
DF <- merge(BDFm_sd, activitylabels, by='subjectnum', all.x = TRUE)

## Creating new tidy data 
DFfinal <- aggregate( .~subjectnum + activity.y, data =  DF, mean)
DFfinal <- DFfinal[order(DFfinal$activity.y, DFfinal$subjectnum),]

## Rename
newnames <- names(DFfinal)
newnames <- sub("^t", "Time", newnames) 
newnames <- sub("^f", "Frequency", newnames)
newnames <- sub("Acc+", "Acceleration", newnames) 
newnames <- sub("Gyro+", "Gyroscope", newnames) 
newnames <- sub("std+", "StandardDeviation", newnames)
colnames(DFfinal) <- newnames
DFfinal <- DFfinal[-c(3)]
```

### Variables 

The final dataset was created with the following variables, I assigned each and every one of them the activity name and the subject that corresponds each activity and substituted some characters for words as shown below:

- t <- Time
- f <- Frequency
- Acc <- Acceleration
- Gyro <- Gyroscope
- std <- StandardDeviation

 [1] "subjectnum"                                              
 [2] "activity.y"                                              
 [3] "TimeBodyAcceleration-mean()-X"                           
 [4] "TimeBodyAcceleration-mean()-Y"                           
 [5] "TimeBodyAcceleration-mean()-Z"                           
 [6] "TimeBodyAcceleration-StandardDeviation()-X"              
 [7] "TimeBodyAcceleration-StandardDeviation()-Y"              
 [8] "TimeBodyAcceleration-StandardDeviation()-Z"              
 [9] "TimeGravityAcceleration-mean()-X"                        
[10] "TimeGravityAcceleration-mean()-Y"                        
[11] "TimeGravityAcceleration-mean()-Z"                        
[12] "TimeGravityAcceleration-StandardDeviation()-X"           
[13] "TimeGravityAcceleration-StandardDeviation()-Y"           
[14] "TimeGravityAcceleration-StandardDeviation()-Z"           
[15] "TimeBodyAccelerationJerk-mean()-X"                       
[16] "TimeBodyAccelerationJerk-mean()-Y"                       
[17] "TimeBodyAccelerationJerk-mean()-Z"                       
[18] "TimeBodyAccelerationJerk-StandardDeviation()-X"          
[19] "TimeBodyAccelerationJerk-StandardDeviation()-Y"          
[20] "TimeBodyAccelerationJerk-StandardDeviation()-Z"          
[21] "TimeBodyGyroscope-mean()-X"                              
[22] "TimeBodyGyroscope-mean()-Y"                              
[23] "TimeBodyGyroscope-mean()-Z"                              
[24] "TimeBodyGyroscope-StandardDeviation()-X"                 
[25] "TimeBodyGyroscope-StandardDeviation()-Y"                 
[26] "TimeBodyGyroscope-StandardDeviation()-Z"                 
[27] "TimeBodyGyroscopeJerk-mean()-X"                          
[28] "TimeBodyGyroscopeJerk-mean()-Y"                          
[29] "TimeBodyGyroscopeJerk-mean()-Z"                          
[30] "TimeBodyGyroscopeJerk-StandardDeviation()-X"             
[31] "TimeBodyGyroscopeJerk-StandardDeviation()-Y"             
[32] "TimeBodyGyroscopeJerk-StandardDeviation()-Z"             
[33] "TimeBodyAccelerationMag-mean()"                          
[34] "TimeBodyAccelerationMag-StandardDeviation()"             
[35] "TimeGravityAccelerationMag-mean()"                       
[36] "TimeGravityAccelerationMag-StandardDeviation()"          
[37] "TimeBodyAccelerationJerkMag-mean()"                      
[38] "TimeBodyAccelerationJerkMag-StandardDeviation()"         
[39] "TimeBodyGyroscopeMag-mean()"                             
[40] "TimeBodyGyroscopeMag-StandardDeviation()"                
[41] "TimeBodyGyroscopeJerkMag-mean()"                         
[42] "TimeBodyGyroscopeJerkMag-StandardDeviation()"            
[43] "FrequencyBodyAcceleration-mean()-X"                      
[44] "FrequencyBodyAcceleration-mean()-Y"                      
[45] "FrequencyBodyAcceleration-mean()-Z"                      
[46] "FrequencyBodyAcceleration-StandardDeviation()-X"         
[47] "FrequencyBodyAcceleration-StandardDeviation()-Y"         
[48] "FrequencyBodyAcceleration-StandardDeviation()-Z"         
[49] "FrequencyBodyAcceleration-meanFreq()-X"                  
[50] "FrequencyBodyAcceleration-meanFreq()-Y"                  
[51] "FrequencyBodyAcceleration-meanFreq()-Z"                  
[52] "FrequencyBodyAccelerationJerk-mean()-X"                  
[53] "FrequencyBodyAccelerationJerk-mean()-Y"                  
[54] "FrequencyBodyAccelerationJerk-mean()-Z"                  
[55] "FrequencyBodyAccelerationJerk-StandardDeviation()-X"     
[56] "FrequencyBodyAccelerationJerk-StandardDeviation()-Y"     
[57] "FrequencyBodyAccelerationJerk-StandardDeviation()-Z"     
[58] "FrequencyBodyAccelerationJerk-meanFreq()-X"              
[59] "FrequencyBodyAccelerationJerk-meanFreq()-Y"              
[60] "FrequencyBodyAccelerationJerk-meanFreq()-Z"              
[61] "FrequencyBodyGyroscope-mean()-X"                         
[62] "FrequencyBodyGyroscope-mean()-Y"                         
[63] "FrequencyBodyGyroscope-mean()-Z"                         
[64] "FrequencyBodyGyroscope-StandardDeviation()-X"            
[65] "FrequencyBodyGyroscope-StandardDeviation()-Y"            
[66] "FrequencyBodyGyroscope-StandardDeviation()-Z"            
[67] "FrequencyBodyGyroscope-meanFreq()-X"                     
[68] "FrequencyBodyGyroscope-meanFreq()-Y"                     
[69] "FrequencyBodyGyroscope-meanFreq()-Z"                     
[70] "FrequencyBodyAccelerationMag-mean()"                     
[71] "FrequencyBodyAccelerationMag-StandardDeviation()"        
[72] "FrequencyBodyAccelerationMag-meanFreq()"                 
[73] "FrequencyBodyBodyAccelerationJerkMag-mean()"             
[74] "FrequencyBodyBodyAccelerationJerkMag-StandardDeviation()"
[75] "FrequencyBodyBodyAccelerationJerkMag-meanFreq()"         
[76] "FrequencyBodyBodyGyroscopeMag-mean()"                    
[77] "FrequencyBodyBodyGyroscopeMag-StandardDeviation()"       
[78] "FrequencyBodyBodyGyroscopeMag-meanFreq()"                
[79] "FrequencyBodyBodyGyroscopeJerkMag-mean()"                
[80] "FrequencyBodyBodyGyroscopeJerkMag-StandardDeviation()"   
[81] "FrequencyBodyBodyGyroscopeJerkMag-meanFreq()"

### Final dataset 

The following dataset already has the changed names and corrections of the whole project, it contains 6 observations and 81 variables.

```{r}
kable(DFfinal) %>%
  kable_styling() %>%
  scroll_box(width = "1000px", height = "300px")
```
